AP/PA Tables ITHIM Global

### 2023-12-12 summary_tables_PA_AP.Rmd

# - desc_stats.csv file (results/multi_city/AP/desc_stats.csv) containing the summary statistics of individual PM2.5 exposure levels, the total PM2.5 concentrations levels, the change in PM2.5 concentration levels compared to the reference scenario and the total transport related CO2 emission concentrations for each scenario and city

# - desc_stats.xlsx file (results/multi_city/AP/desc_stats.xlsx) containing the following tabs:

>>>>

# - desc_stats.csv file (results/multi_city/AP/desc_stats.csv, also saved with output_version number in file name) containing the summary statistics of individual PM2.5 exposure levels, the total PM2.5 concentrations levels, the change in PM2.5 concentration levels compared to the reference scenario and the total transport related CO2 emission concentrations for each scenario and city

# - desc_stats_*output_version*.xlsx file (results/multi_city/AP/desc_stats_*output_version*.xlsx) containing the following tabs:
